Approximating the Optimal State Abstraction

### 2016-04-30 icml_workshop/desiderata.tex
Touched up Dave's desidarata section

Critically, either desiderata is trivial to satisfy on its own.

Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state from $S_G$. Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP.

Now consider \textsc{Optimality}. Again, consider the following uninteresting method; generate an MDP $M_A$, such that $M_A$ is identical to $M_G$. Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.

In isolation, either is trivially satisfiable.

The interesting (and difficult) case is satisfying {\it both} desiderata. To the best of our knowledge, no theory of temporal abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata. After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.

>>>>

Critically, either desiderata is trivial to satisfy on its own. Given an \ac{MDP}, $M_G$, we can satisfy \textsc{Compressibility} by replacing $S_G$ with a state space that consists of a single (arbitrary) state and a single (arbitrary action). Clearly, such a resulting \ac{MDP} satisfies our first desiderata - we are left with an MDP that is substantially smaller than the original MDP. Now consider \textsc{Optimality}. Again, consider the following uninteresting method; generate an MDP $M_A$, such that $M_A$ is identical to $M_G$. Thus, the optimal policy for $M_A$ is exactly the optimal policy for $M_G$, consequently satisfying \textsc{Optimality}.

The interesting (and difficult) case is satisfying {\it both} desiderata. To the best of our knowledge, no abstraction has been formally proven to satisfy the two - in the next section, we discuss prior methods of abstraction, and their relative status to these desiderata. After, we propose an extension of some prior work that suggests how such results may be obtained for temporal abstraction.
